Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-30 manuscript/manuscript.Rmd
Update for new data workflow

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
```

@@

XXX: Use r package captioner for captions

@@

tmp <- no_st %>% filter(family == "Aca", mark %in% c("A1", "A2"))

@@

```{r knitcitations_write, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
mendbib <- RCurl::getURL("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=1", .opts=RCurl::curlOptions(followlocation=TRUE))
cat(mendbib, file="library.bib")
```

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
```

@@

@@

@@

```{r knitcitations_write, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
mendbib <- RCurl::getURL("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=1", .opts=RCurl::curlOptions(followlocation=TRUE), ssl.verifypeer = FALSE)
cat(mendbib, file="library.bib")
```
